%-------------------------
% Academic CV - Kitae Kim
% Clean format (DK-style)
%-------------------------

\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[normalem]{ulem}
\usepackage{array}
\usepackage{ragged2e}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue}

% Section: uppercase, bold, rule below, compact
\titleformat{\section}{\normalsize\bfseries\MakeUppercase}{}{0em}{}
\titlespacing{\section}{0pt}{10pt}{5pt}
\newcommand{\sectionrule}{\vspace{-2pt}\rule{\linewidth}{0.4pt}\vspace{4pt}}

\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titlespacing{\subsection}{0pt}{6pt}{3pt}

% Left column width: unified across Positions, Education, Industry, Teaching
\newlength{\leftcolwidth}
\setlength{\leftcolwidth}{2.2cm}

% Lists: minimal spacing
\setlist{noitemsep, topsep=0pt, leftmargin=1.2em, itemindent=0pt, labelsep=0.35em}
\setlist[itemize]{label=\textbullet}

\newlength{\cvlabelwidth}
\setlength{\cvlabelwidth}{6.5em}

% Position block: left = date only (no italic), right = content
\newcommand{\posblock}[2]{%
  \par\noindent
  \begin{minipage}[t]{\leftcolwidth}
    \raggedright #1
  \end{minipage}%
  \hspace{0.8em}%
  \begin{minipage}[t]{\dimexpr\linewidth-\leftcolwidth-0.8em\relax}
    \raggedright
    #2
  \end{minipage}\par\vspace{0.8em}%
}

% Education block: left = year range only (no italic), right = degree + institution + GPA + advisor
\newcommand{\edublock}[2]{%
  \par\noindent
  \begin{minipage}[t]{\leftcolwidth}
    \raggedright #1
  \end{minipage}%
  \hspace{0.8em}%
  \begin{minipage}[t]{\dimexpr\linewidth-\leftcolwidth-0.8em\relax}
    \raggedright
    #2
  \end{minipage}\par\vspace{0.6em}%
}

% Industry block: left = year only (no italic), right = org name + Project/Role/Results
\newcommand{\industryblock}[2]{%
  \par\noindent
  \begin{minipage}[t]{\leftcolwidth}
    \raggedright #1
  \end{minipage}%
  \hspace{0.8em}%
  \begin{minipage}[t]{\dimexpr\linewidth-\leftcolwidth-0.8em\relax}
    \raggedright
    #2
  \end{minipage}\par\vspace{0.6em}%
}

% Teaching block: left = year (no italic), right = TA + course + institution + term
\newcommand{\teachingblock}[2]{%
  \par\noindent
  \begin{minipage}[t]{\leftcolwidth}
    \raggedright #1
  \end{minipage}%
  \hspace{0.8em}%
  \begin{minipage}[t]{\dimexpr\linewidth-\leftcolwidth-0.8em\relax}
    \raggedright
    #2
  \end{minipage}\par\vspace{0.4em}%
}

\begin{document}

%---------- Header ----------
\begin{center}
  {\LARGE \textbf{Kitae Kim}}\\[4pt]
  Assistant Professor\\
  School of Business, Korea Aerospace University\\
  Gyeonggi-do, 12921, Republic of Korea\\[2pt]
  \href{mailto:kitaekim@kau.ac.kr}{kitaekim@kau.ac.kr} \ $|$ \ \href{mailto:kitaekim0819@gmail.com}{kitaekim0819@gmail.com}
\end{center}
\vspace{6pt}

%---------- Positions ----------
\section{Positions Held}\sectionrule

\posblock{2026--Present}{\textbf{Assistant Professor}\\
  School of Business, Korea Aerospace University, Gyeonggi-do, Republic of Korea}

\posblock{2025--2026}{\textbf{Postdoctoral Researcher}\\
  Korea Institute of Science and Technology Information (KISTI), Daejeon, Republic of Korea
  \begin{itemize}
    \item Led LLM-based semantic search system development for data platforms
    \item Developed causal discovery and deep learning--based decision support system for semiconductor manufacturing
  \end{itemize}}

%---------- Education ----------
\section{Education}\sectionrule

\edublock{2021--2025}{\textbf{Ph.D.\ in Management Engineering} (Focus: Information Systems)\\
  Korea Advanced Institute of Science and Technology (KAIST), Seoul\\
  GPA: 3.91/4.3 \ $|$ \ Advisor: Prof.\ Sung-Hyuk Park}

\edublock{2018--2020}{\textbf{M.S.\ in Management Engineering}\\
  KAIST, Seoul\\
  GPA: 3.82/4.3 \ $|$ \ Advisor: Prof.\ Yong-Jin Hyun}

\edublock{2013--2017}{\textbf{B.S.\ in Civil \& Environmental Engineering}\\
  Korea University, Seoul\\
  GPA: 3.85/4.5\ $|$ \ Graduated with Honors}

%---------- Research Interests ----------
\section{Research Interests}\sectionrule

Machine Learning, Causal Inference, Agentic AI, Human-AI Collaboration, Digital Platform Design, Digital Marketing Analytics, Operation Optimization

%---------- Research Papers ----------
\section{Research Papers and Work-in-Progress}\sectionrule

\subsection{Under Review}
\begin{itemize}
  \item \textbf{Kim K.}, Lee M., Park SH., Park SJ., \textit{Optimizing Media Planning: Multimethod Evidence of a Prescriptive Media Budget Allocation Framework (MBAF).} Presented at HICSS 2022. Under 1\textsuperscript{st} round review at \textit{International Journal of Advertising}.
  \item Kwon S., \textbf{Kim K.}, Park SH., \textit{Shorter, Newer? How Monetization Reshapes Creator Strategy on YouTube Shorts.} Presented at KrAIS Summer Workshop 2023. Under 2\textsuperscript{nd} round review at \textit{Internet Research}.
\end{itemize}

\subsection{Work in Progress}
\begin{itemize}
  \item \textbf{Kim K.}, Lee D., Park SH., Sim J., \textit{Digital Rule of Thumb: Impact of Autocomplete in Search Engines across Mobile and Personal Computer Channels} (SSRN: 5001062, 2024). Presented at SCECR 2022, INFORMS WDS 2022, ICIS 2022, WISE 2025; target: \textit{Information Systems Research}.
  \item \textbf{Kim K.}, Lee M., Park SH., \textit{DMMM: Deep Marketing Mix Modeling and Optimal Budget Allocation.} Presented at INFORMS International 2025, AMCIS 2025; target: \textit{Management Science}.
\end{itemize}

\subsection{Other Peer-Reviewed Publications}
\begin{itemize}
  \item Lee, S., \textbf{Kim, K.}, Y.\ J., Park, B. (2025). Evaluating sponsorship effects influenced by involuntary media multitasking: Neuromarketing approach. \textit{International Journal of Applied Sports Sciences}.
  \item Cho, H., \textbf{Kim, K.}, Lee, S. (2025). Mood transfer research between program and advertisement: Applying neuro-marketing. \textit{Journal of the Korea Convergence Society}.
  \item Lee, S., \textbf{Kim, K.}, Hyun, Y.\ J., \& Park, B. (2024). From sensation to emotion: A neuromarketing study of sport sponsorship effects. \textit{Sport Marketing Quarterly}, 33(2), 99--115.
  \item Lee, S.\ H., Hyun, Y.\ J., Park, B., \textbf{Kim, K.}, \& Kwun, Y.\ Y. (2022). How a sensational event influences sponsorship effects: Applying neuromarketing. \textit{Korean Journal of Sport Science}, 33(3), 451--463.
\end{itemize}

%---------- Conference Presentations ----------
\section{Conference Presentations}\textit{(Presenter \uline{underlined})}\\
\sectionrule\\
\begin{itemize}
  \item \textbf{\uline{Kim K.}}, Lee M., Park SH. (2025). DMMM: Deep Marketing Mix Model for Optimal Budget Allocation. \textit{AMCIS}, Montr\'eal, Canada.
  \item \textbf{\uline{Kim K.}}, Lee M., Park SH. (2025). 4M: Machine Learning Based Marketing Mix Model. \textit{INFORMS International}, Singapore.
  \item \textbf{\uline{Kim K.}}, Lee M., Park SH. (2025). Toward a Machine Learning Marketing Mix Model. \textit{KrAIS Summer Workshop}, Busan, Korea.
  \item \textbf{\uline{Kim K.}}, Lee D., Park SH., Sim J. (2023). Modalities and Search Costs: A Case of Autocomplete. \textit{KrAIS Summer Workshop}, Seoul, Korea.
  \item \uline{Kwon S.}, \textbf{Kim K.}, Park SH. (2023). Does Money Make Creators Work Harder? \textit{KrAIS Summer Workshop}, Seoul, Korea.
  \item \textbf{Kim K.}, Lee D., Park SH., \uline{Sim J.} (2022). Modalities and Search Costs: A Case of Autocomplete in Search Engine. \textit{POST-ICIS KrAIS Workshop}, Copenhagen, Denmark.
  \item \textbf{\uline{Kim K.}}, Lee D., Park SH., Sim J. (2022). Digital Rule of Thumb: A Natural Experiment on Autocomplete in Search Engines. \textit{ICIS}, Copenhagen, Denmark \textbf{(Travel Grant, KAIST)}.
  \item \textbf{\uline{Kim K.}}, Lee D., Park SH., Sim J. (2022). Digital Rule of Thumb: A Natural Experiment on Autocomplete in Search Engines. \textit{INFORMS Workshop on Data Science}, Indianapolis, IN, USA.
  \item \textbf{\uline{Kim K.}}, Park SH. (2022). How to Choose the Right Person? Social Media Marketing Optimization Framework. \textit{ICEC}, Daegu, Korea \textbf{(Best Research-in-Progress Paper)}.
  \item \textbf{\uline{Kim K.}}, Lee D., Park SH., Sim J. (2022). Digital Rule of Thumb: A Natural Experiment on Autocomplete in Search Engines. \textit{SCECR}, Madrid, Spain.
  \item Park SH., \uline{Lee M.}, \textbf{Kim K.}, Shin D. (2022). A Nonlinear Optimization Model of Advertising Budget Allocation across Multiple Digital Media Channels. \textit{HICSS}, Online.
  \item Park SH., \uline{Lee M.}, \textbf{Kim K.}, Shin D. (2021). Nonlinear Optimization Model of Advertising Budget Allocation across Multiple Digital Media Channels. \textit{SCECR}, Online.
\end{itemize}

%---------- Industry Research Collaborations ----------
\section{Industry Collaborations}\sectionrule

\industryblock{2024--Present}{\textbf{Wharton AI \& Analytics Initiative (WAIAI) \& Google}
\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{Project:} Response modeling with aggregate and event-level data
  \item \makebox[\cvlabelwidth][l]{Role:} Submitted research proposal on deep learning--based marketing mix models and derivative-free optimization for budget allocation
  \item \makebox[\cvlabelwidth][l]{Results:} In progress
\end{itemize}}

\industryblock{2023--Present}{\textbf{ImpactAI}
\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{Project:} Deep learning--based marketing mix models and optimal budget allocation framework
  \item \makebox[\cvlabelwidth][l]{Role:} Developed ML/DL marketing mix models and budget allocation strategy using derivative-free optimization
  \item \makebox[\cvlabelwidth][l]{Results:} +30\% prediction accuracy; +10\% return on marketing spend
\end{itemize}}

\industryblock{2022--2023}{\textbf{UNICEF Korea}
\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{Project:} Optimal advertising budget allocation across traditional and digital channels (donor lifetime value)
  \item \makebox[\cvlabelwidth][l]{Role:} Analyzed 10-year advertising efficiency across UNICEF Korea marketing channels; recommended budgeting strategies
  \item \makebox[\cvlabelwidth][l]{Results:} +7\% donors' lifetime donation
\end{itemize}}

\industryblock{2021--2022}{\textbf{PTKorea}
\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{Project:} Advertising sales prediction for Samsung online store
  \item \makebox[\cvlabelwidth][l]{Role:} Developed ML sales prediction algorithm and simulation with marketing activities
  \item \makebox[\cvlabelwidth][l]{Results:} SKU-level prediction +30\% accuracy vs.\ baseline
\end{itemize}}

\industryblock{2021}{\textbf{Kyobo Book}
\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{Project:} Deep learning sales forecasting system for books
  \item \makebox[\cvlabelwidth][l]{Role:} Designed data pipeline and policy; developed LSTM-based SKU-level forecasting
  \item \makebox[\cvlabelwidth][l]{Results:} +30\% forecasting accuracy
\end{itemize}}

\industryblock{2020--2022}{\textbf{REVU Corporation}
\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{Project:} Optimal influencer portfolio recommendation for social media marketing
  \item \makebox[\cvlabelwidth][l]{Funding:} $\sim$\$100K grant (Korea Ministry of SMEs and Startups)
  \item \makebox[\cvlabelwidth][l]{Role:} Led end-to-end ML solution for influencer portfolio selection
  \item \makebox[\cvlabelwidth][l]{Results:} +15\% KPI in field experiments (Korea \& Taiwan)
\end{itemize}}

\industryblock{2020}{\textbf{Eigene Korea}
\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{Project:} Deep learning--based recommender systems
  \item \makebox[\cvlabelwidth][l]{Role:} Developed Item2Vec-based recommendation algorithm for beauty products
  \item \makebox[\cvlabelwidth][l]{Results:} Model deployed in production
\end{itemize}}

%---------- Teaching ----------
\section{Teaching}\sectionrule
\begin{itemize}
  \item Financial Data Analytics, Teaching Assistant -- KAIST, Spring 2021, Spring 2022
  \item IT-based Business Innovation, Teaching Assistant -- KAIST, Fall 2021
  \item IT Management, Teaching Assistant -- KAIST, Fall 2022
  \item IT Strategy and Business (Executive MBA), Teaching Assistant -- KAIST, Fall 2023
  \item Introduction to AI and ML, Teaching Assistant -- KAIST, Spring 2024
  \item IT System Design, Teaching Assistant -- KAIST, Fall 2024
\end{itemize}

%---------- Mentorship ----------
\section{Mentorship}\sectionrule

Mentored two master's students on thesis projects applying data analytics and causal inference in real-world business contexts.
\begin{itemize}
  \item Causal impact of same-day delivery on sales and returns by product category (DiD \& Matching, 2024)
  \item Spillover effects of short-form video content on platform engagement (Staggered DiD \& Matching, 2025)
\end{itemize}

%---------- Coursework ----------
\section{Coursework Training}\sectionrule

\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{\textbf{Methods:}} Econometrics, Applied Econometrics, Probability and Statistics, Behavioral Science Research Methods, Business Modeling, IT Management Seminars
  \item \makebox[\cvlabelwidth][l]{\textbf{Theory:}} IT Management, Industrial Organization, Marketing Theory, Consumer Behavior Theories, Advanced Marketing Issues
\end{itemize}

%---------- Technical Skills ----------
\section{Technical Skills}\sectionrule

\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{\textbf{Programming:}} Python, SQL
  \item \makebox[\cvlabelwidth][l]{\textbf{Data Analysis:}} STATA
  \item \makebox[\cvlabelwidth][l]{\textbf{Deep Learning:}} PyTorch, TensorFlow
  \item \makebox[\cvlabelwidth][l]{\textbf{Optimization:}} CVXPY, Optuna
  \item \makebox[\cvlabelwidth][l]{\textbf{Productivity:}} MS Word, Excel, PowerPoint
\end{itemize}

%---------- Academic Service ----------
\section{Academic Service}\sectionrule

\begin{itemize}
  \item \makebox[\cvlabelwidth][l]{\textbf{Ad-hoc Review:}} ICIS, AMCIS, PACIS, WITS, CIST, KrAIS
  \item \makebox[\cvlabelwidth][l]{\textbf{Award:}} Best Reviewer, KrAIS Summer Workshop, 2025
\end{itemize}

\end{document}
